Deciding to Disclose

### 2015-01-07 Abstract.tex
More Springer jazz
Grayscale friendliness, spelling

\pdfbookmark[1]{Abstract}{Abstract}

@@

The primary purpose of this work is to demonstrate the significance of precisely how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, supported by the use of statistical emulators for a full exploration of the parameter space.
We also demonstrate the utility of an approach which it is hoped goes some way towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents. To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends reported in the literature.

@@

We employ game theory to define a signalling game representative of a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment. This game is then recast as two games played against \enquote{nature}, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser with full access to the structure of the decision problem, and a \ac{CPT} rule.

In simulation, we recreate two key qualitative trends described in the Midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
Finally a global sensitivity analysis using \acp{GEM} was conducted, to compare the response surfaces of the different decision rules in the game.

>>>>

@@

The primary purpose of this work is to demonstrate the significance of how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, the analysis is supported by the use of statistical emulators for a full exploration of the parameter space.
We also demonstrate the utility of an approach which it is hoped contributes towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents. To this end we aim to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends reported in the literature.

@@

We employ a game theoretic framework to define a signalling game. The game represents a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment. This game is then recast as two games played against \enquote{nature}, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser with full access to the structure of the decision problem, and a \ac{CPT} rule.

In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game.

### 2015-01-07 Background.tex
Grayscale friendliness, spelling

Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explaination of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

Other work augments the signalling game model, for example \citet{Austen-Smith2005} add a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}. On a similar tack, \citet{Feltovich2002} introduce additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality fail to do so.

@@

While game theory addresses rational strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. An alternative view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

>>>>

Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e. more, or louder chirping) carries a risk of being eaten by predators. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

Other work augments the signalling game model, for example \citet{Austen-Smith2005} add a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subsequent empirical support for the idea from \citet{Jr2010}. On a similar tack, \citet{Feltovich2002} introduce additional noisy type information, finding that this effectively explained counter-intuitive observed behaviour where actors with every right to boast of their quality fail to do so.

@@

While game theory addresses rational strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. An complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

### 2015-01-07 Conclusion.tex
Grayscale friendliness, spelling

One of the notable features of the results is the similarity in behaviour of the two classes of decision rule. To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model. To some extent this might be anticipated, in that the payoffs are clearly unrealistic, which limits the utility of the \ac{CPT} approach.  Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogenous here. In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.  With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.  This, together with the variablility associated with the heuristic type decision rules speaks to a tradeoff between capturing reality, and replicating it.

Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is clearly a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later. In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g. exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT} like model of \citet{Loewenstein1992}, is warranted.

As noted in section \ref{sub:sensitivity}, the impact of information sharing between midwives is surprisingly minimal, where it might be expected to play a more significant role in reality. A possible explanation for this lies in the implementation, which may place an excessive constraint on how much information midwives can share. The restriction to sharing only after a referral, together with the disparity in population sizes, and random allocation of appointments leads to midwives rarely having more than a single interaction with woman to pass on to their colleagues. Furthermore, because midwives are only informed of the true type if a referral occurs, they have an inherent myopia, since until they have evidence of deception they will not refer, with said evidence difficult to obtain without a referral.

In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about particular women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing innapropriately to variance in output.

@@

The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model. While qualitative trends offer some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure.  As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy. 
With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are borne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy. By contrast, if one takes the view that a Lexicographic model is a better approximation of real behaviour, then outcomes can best be influenced by controlling how far midwives punish their women socially. We would however suggest that there are better reasons than the outputs of a simulation for doing so.

>>>>

One of the notable features of the results is the similarity in behaviour of the two classes of decision rule. To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model. This might be to a degree anticipated, in that the payoffs are unrealistic, which limits the utility of the \ac{CPT} approach.  Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here. In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.  With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.  This, together with the variability associated with the heuristic type decision rules speaks to a trade off between capturing reality, and replicating it.

Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later. In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g. exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT} like model of \citet{Loewenstein1992}, is warranted.

As noted in section \ref{sub:sensitivity}, the impact of information sharing between midwives is surprisingly minimal, where it might be expected to play a more significant role in reality. A possible explanation for this lies in the implementation, which may place an excessive constraint on how much information midwives can share. The restriction to sharing only after a referral, together with the disparity in population sizes, and random allocation of appointments leads to midwives rarely having more than a single interaction with woman to pass on to their colleagues. Furthermore, because midwives are only informed of the true type if a referral occurs, they have an inherent myopia since until they have evidence of deception they will not refer, with said evidence difficult to obtain without a referral.

In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about particular women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

@@

The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model. While qualitative trends offer some indication, they are limited in scope, and do not permit strong claims about the drivers of disclosure.  As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy. 
With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are borne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy. By contrast, if one takes the view that a Lexicographic model is a better approximation of real behaviour, then outcomes can best be influenced by controlling how far midwives punish their women socially. We would however suggest that there are better reasons than the outputs of a simulation for doing so.

### 2015-01-07 Introduction.tex
Grayscale friendliness, spelling

The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly (e.g. \citet{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others). As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

@@

While there is no universal theory of human behaviour to sit at the center of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, decision rules represent a pleasingly parsimonious alternative to explicit behavioural rules covering all possible eventualities.

Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is decision making. Taking a balance between the strongly biological, e.g. neural networks, and the more abstract threshold, or microsimulation like models yields a computationally tractable approach. Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.

>>>>

The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g. \citet{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others). As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

@@

While there is no universal theory of human behaviour to sit at the centre of \ac{ABM}ing as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, decision rules represent a pleasingly parsimonious alternative to explicit behavioural rules covering all possible eventualities.

Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is decision making. Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away yields a computationally tractable approach. Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.

### 2015-01-07 Methods.tex
Grayscale friendliness, spelling

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parameterisation for the model (e.g. \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work. For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}. The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty. Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.

@@

\begin{table}[h!]
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwife & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
\(\delta\) & Probability weighting for losses &  0.69\\ \hline
\(\alpha\) & Power for gains  & 0.88 \\ \hline
\(\beta\) & Power for losses & 0.88 \\ \hline
\(\lambda\) & Loss aversion &  2.25 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1\}\), with 100 runs under each condition.

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs. The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem. The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propogates to uncertainty in the output, and how sharply the output responds to change in each parameter.

@@

Sixteen emulators were built, covering each of the four outputs on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(x_{h} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

>>>>

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parametrisation for the model (e.g. \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work. For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}. The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty. Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.

@@

\begin{table}[h!]
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwife & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ \hline
\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
\(\delta\) & Probability weighting for losses &  0.69\\ \hline
\(\alpha\) & Power for gains  & 0.88 \\ \hline
\(\beta\) & Power for losses & 0.88 \\ \hline
\(\lambda\) & Loss aversion &  2.25 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs. The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem and then serves as an emulator for the simulator. The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.

@@

Sixteen emulators were built, covering each of the four outputs on all four decision models. These emulators were used to conduct a probabilistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(x_{h} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}
